---
title: "Practical Machine Learning Project"
author: "Min Woo Tommy Kim"
date: "13/07/2020"
output: html_document
---

```{r, include=FALSE}

library(caret)
library(rpart)
library(rpart.plot)
library(rattle)
library(RColorBrewer)
library(randomForest)
library(gbm)

memory.size()
memory.limit()
memory.limit(100000)
memory.size()
memory.limit()

```

[Data]
Importing Datasets

```{r}
##Importing Datasets

Train_Data <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"))
dim(Train_Data)

Test_Data <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"))
dim(Test_Data)
```

[Data Adjustment]
Adjusting Data to eliminate the columns those are having NA and values close to 0
```{r}

Train_Data_Adj <- Train_Data[, -nearZeroVar(Train_Data)]
dim(Train_Data_Adj)

Test_Data_Adj <- Test_Data[, -nearZeroVar(Train_Data)]
dim(Test_Data_Adj)

Train_Data_Adj_Final <- Train_Data_Adj[, colSums(is.na(Train_Data_Adj)) == FALSE]
dim(Train_Data_Adj_Final)

Test_Data_Adj_Final <- Test_Data_Adj[, colSums(is.na(Train_Data_Adj)) == FALSE]
dim(Test_Data_Adj_Final)

```

[Data Adjustment]
Removing Columns with Unique Identifier & those are not numeric
```{r}
Train_Data_Final <-Train_Data_Adj_Final[, 7:59]
dim(Train_Data_Final)
Test_Data_Final <-Test_Data_Adj_Final[, 7:59]
dim(Test_Data_Final)
```

Splitting Train_Data_Final into 'training' (70%) and 'testing' (30%)
```{r}
inTrain <- createDataPartition(Train_Data_Final$classe, p=0.7, list=FALSE)
training <-Train_Data_Final[inTrain,]
dim(training)
testing <- Train_Data_Final[-inTrain,]
dim(testing)
```

[Modeling] Decision Tree
```{r}
set.seed(323)
Model_DT <- train(classe ~. , data=training, method= "rpart")
fancyRpartPlot(Model_DT$finalModel)

Predict_DT <- predict(Model_DT, testing)
DT_Result <- confusionMatrix(Predict_DT, testing$classe)
DT_Result
```

[Modeling] Generalized Boosted Regression Model
```{r}
set.seed(323)
Model_GBM <- train(classe ~. , data=training, method= "gbm", verbose = FALSE)
Model_GBM$finalModel
print(Model_GBM)

Predict_GBM <- predict(Model_GBM, testing)
GBM_Result <- confusionMatrix(Predict_GBM, testing$classe)
GBM_Result
```

Configuring parallel processing
```{r}
library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1)
registerDoParallel(cluster)
```

Configuring trainControl object
```{r}
fitControl <- trainControl(method = "cv", number = 5, allowParallel = TRUE)
memory.limit(100000)
```

[Modeling] Random Forest
```{r}
set.seed(323)
Model_RF <- train(classe ~. , data=training, method= "rf", trControl = fitControl)
Model_RF$finalModel

Predict_RF <- predict(Model_RF, testing)
RF_Result <- confusionMatrix(Predict_RF, testing$classe)
RF_Result
```

De-registering parallel processing cluster
```{r}
stopCluster(cluster)
registerDoSEQ()
```

Conducting final prediction by using Random Forest model, which has the highest accuracy among the models
```{r}
predict(Model_RF, Test_Data_Final)
```